Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor

### 2020-10-14 docs/paper/paper.tex
* Reviewer 1 reply is finished

		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset.
		\\\hl{$ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 $ $ d1 = 0.45 um $ $ d2= 0.75 um$ $ d3 = 0.35 um $.}\\ \hl{ $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.75um $ $ d3 = 0.35um $.}		
		  }
	\end{subfigure}
	\caption{Testing results without GAN augmentation phase}
	\label{chart:perfnoaug}
\end{figure*}

@@

		\addlegendimage{first}\addlegendentry{Without GAN:0.32373}
		\addlegendimage{second}\addlegendentry{With GAN:0.08664 }
		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset. 
		\\ \hl{$n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 um $ $ d1 = 0.45 um $ $ d2= 0.75um $ $ d3 = 0.35um $.} \\ \hl{$n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.55um $ $ d3 = 0.15um $.} 
		}
	\end{subfigure}
	\caption{GAN Phase experimental results}
	\label{chart:ganperf}
\end{figure*}

@@

In this paper, we have demonstrated that the use of generative adversarial networks can be beneficial to neural networks that are designed to compute propagation characteristics of PCF devices. Additionally, we have also proposed and demonstrated a neural network that is both more generic and more accurate to estimate the confinement loss compared to the state-of-the-art network. The GAN phase also reduces the required samples to fully train the ANN, reducing the work necessary to employ the proposed system. The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research article. \hl{The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research; in the experiments, it surpassed the accuracy of the method proposed in }\cite{paper0}\hl{ on the dataset that method is optimized on.}

>>>>

		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset.
		\\\hl{Left: $ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 $ $ d1 = 0.45 um $ $ d2= 0.75 um$ $ d3 = 0.35 um $.}\\ \hl{Right: $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.75um $ $ d3 = 0.35um $.}		
		  }
	\end{subfigure}
	\caption{Testing results without GAN augmentation phase}
	\label{chart:perfnoaug}
\end{figure*}

@@

		\addlegendimage{first}\addlegendentry{Without GAN:0.32373}
		\addlegendimage{second}\addlegendentry{With GAN:0.08664 }
		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset. 
		\\ \hl{Left: $n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 um $ $ d1 = 0.45 um $ $ d2= 0.75um $ $ d3 = 0.35um $.} \\ \hl{Right: $n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 um $ $ d1 = 0.25 um $ $ d2= 0.55um $ $ d3 = 0.15um $.} 
		}
	\end{subfigure}
	\caption{GAN Phase experimental results}
	\label{chart:ganperf}
\end{figure*}

@@

In this paper, we have demonstrated that the use of generative adversarial networks can be beneficial to neural networks that are designed to compute propagation characteristics of PCF devices. Additionally, we have also proposed and demonstrated a neural network that is both more generic and more accurate to estimate the confinement loss compared to the state-of-the-art network. The GAN phase also reduces the required samples to fully train the ANN, reducing the work necessary to employ the proposed system. The proposed combination is shown to be general enough that even though it is designed for the SPR dataset built for this research article. \hl{The proposed combination is shown to be general enough that even though it is designed and optimized for the SPR dataset; in the experiments, it surpassed the accuracy of the method proposed in }\cite{paper0}\hl{ on the dataset that method is optimized on.}
